Class-based network segregation, Economic Inequality and Redistributive Preferences across societies

### 2024-10-22 paper1_jiturra.Rmd
updates patrick v3

dfreg1 <- dfreg %>% dplyr::select(
  egal,
  homclass3_V_res,
  know_total,
  # socialtrust,
  dclass3res_V,
  Q03pcm,
  edyears,
  # dclass3spo_V,  
  workst,
  # union,
  female,
  agenum,
  # religion,
  partner,
  "gini_disp",
  loggdppercapita,
  wstate2,
  abs_red,
  ilo_taxrev,
  ilo_govspe,
  ) 
```

>>>>

dfreg1 <- dfreg %>% dplyr::select(
  egal,
  homclass3_V_res,
  know_total,
  # socialtrust,
  dclass3res_V,
  Q03pcm,
  edyears,
  # dclass3spo_V,  
  workst,
  # union,
  female,
  agenum,
  # religion,
  partner,
  "gini_disp",
  loggdppercapita,
  wstate2
  )

names(dfreg1)
varlab <- 
c("Redistributive preferences","Class-based network homogeneity",
  "Network size","Social class",
  "Household Income","Education in years","Labor market status",
  "Gender","Age in years","Has partner",
  "Income Inequality - Gini Index",
  "GDP/capita ",
  "Size of the welfare state")

sjlabelled::set_label(dfreg1) <- varlab
# names(dfreg) <- varlab

st(dfreg1,labels=T,
   title="Descriptive Statistics for Study Variables",
   out = "viewer",
   digits = 2, 
   factor.counts = F,
   factor.numeric = F,
   summ = list(
     c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'),
     c('notNA(x)','mean(x)')
   ),
   summ.names = list(
     c('N','Mean','SD','Min','Max'),
     c('Count','Percent')   
   ))
